Interpolation of Sparse High-Dimensional Data\thanks {This work was supported by the National Science Foundation Grant CNS-1565314.}

### 2019-03-20 Paper_[2019-02]_Numerical_Algorithms/tchlux-NA-2019.tex
created an affine weights visual. finished NA paper draft. wrote report on Xiaodong clock cycle data.

The remainder of this paper is organized as follows. Sections
\ref{sec:regression} and \ref{sec:interpolation} present the
multivariate models. Section \ref{sec:error} presents the error
measuring methodology that is used for collecting empirical
results. Section \ref{sec:theory} presents the theoretical error
bounds for interpolation. Section \ref{sec:data} presents the data
sets for empirical approximation analysis and presents the
approximation results for all models on these data sets. Section
\ref{sec:discussion} analyzes and discusses the results, their
implications, and their limitations. Finally, Section
\ref{sec:conclusion} concludes.

@@

This section presents the theoretical results bounding the error of
Delaunay interpolation. The error analysis relies on the Delaunay
interpolation for two reasons: (1) second order results can be
obtained utilizing a Lipschitz constant on the gradient of a function,
rather than standard Lipschitz bounds and (2) multiple other
interpolants analyzed compute predictions as convex combinations of
observed function values, which may allow for straight forward
extensions of this error bound.

@@

In summary, the approximation error of a Delaunay interpolant tends
quadratically towards zero when approaching observed data only when
the diameter of the interpolating simplex is also reduced at a
proportional rate. Without the incorporation of additional
observations, only linear convergence to the true function is be
achieved. Notice that the approximation error is largely determined by
the spacing of observed data. Predictions made by simplices whose
vertices are not well-spaced (i.e. have large diameter, or are nearly
contained in a hyperplane) have higher error. In light of this error
bound, an empirical evaluation of presented algorithms follows.

@@

The theoretical results constructed in Section \ref{sec:theory} for
Delaunay interpolation are promising, however they are difficult to
interpret in context with the other approximation algorithms that do
not have similar known uniform error bounds. For that reason, this
paper utilizes five different data sets of varying dimension and
application to construct approximations and compare the accuracy of
different techniques.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-forest-fire.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Area Burned Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the amount of area
    that would be burned given environment conditions. $10$-fold
    cross validation as described in the beginning of Section
    \ref{sec:data} is used to evaluated each algorithm. This results
    in exactly one prediction from each algorithm for each data
    point. These boxes depict the median (middle bar), median $95\%$
    confidence interval (cones), quartiles (box edges), fences at
    $3/2$ interquartile range (whiskers), and outliers (dots) of
    absolute prediction error for each model. Similar to figure
    \ref{fig:hist-forest-fire}, the errors are presented on a natural
    log scale. The complementing numerical data to this figure is
    provided in table \ref{table:error-forest-fire} in the Appendix.}
  \label{fig:error-forest-fire}
\end{figure}

@@

As suggested by figure \ref{fig:error-forest-fire}, the SVR has the
lowest absolute prediction errors for 80\% of the data, with ShepMod
and BoxSpline being the nearest overall competitors. The effectiveness
of SVR on this data suggests the underlying function can be defined by
relatively few parameters, as well as the importance of capturing the
low-burn-area data points.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-weather.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Sydney Rainfall Tomorrow Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the amount of
    rainfall expected on the next calendar day given various sources
    of local meteorological data. $10$-fold cross validation as
    described in the beginning of Section \ref{sec:data} is used to
    evaluated each algorithm. This results in exactly one prediction
    from each algorithm for each data point. These boxes depict the
    median (middle bar), median $95\%$ confidence interval (cones),
    quartiles (box edges), fences at $3/2$ interquartile range
    (whiskers), and outliers (dots) of absolute prediction error for
    each model. The errors are presented on a natural log scale,
    mimicking the presentation in figure \ref{fig:hist-weather}. The
    complementing numerical data to this figure is provided in table
    \ref{table:error-weather} in the Appendix.}
  \label{fig:error-weather}
\end{figure}

@@

While figure \ref{fig:hist-weather} makes MARS look far better than
other techniques, it only provides the best prediction for 11\% of
points. The MLP has the lowest absolute error for 56\% of points and
LSHEP is best for 28\%. MARS likely achieves such a low first quartile
due to the high occurrence of the value 0 in the data.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-credit-card.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Transaction Amount Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the expected
    transaction amount given transformed (and obfuscated) vendor and
    customer-descriptive features. $10$-fold cross validation as
    described in the beginning of Section \ref{sec:data} is used to
    evaluated each algorithm. This results in exactly one prediction
    from each algorithm for each data point. These boxes depict the
    median (middle bar), median $95\%$ confidence interval (cones),
    quartiles (box edges), fences at $3/2$ interquartile range
    (whiskers), and outliers (dots) of absolute prediction error for
    each model. The absolute errors in transaction amount predictions
    are presented on a natural log scale, just as in figure
    \ref{fig:hist-credit-card}. The complementing numerical data to
    this figure is provided in table \ref{table:error-credit-card} in
    the Appendix.}
  \label{fig:error-credit-card}
\end{figure}

@@

As can be seen in figure \ref{fig:error-credit-card}, the MLP
outperforms all other algorithms at the first, second, third, and
fourth quartiles. The MLP produces the lowest absolute error
prediction for 80\% of transactions, Delaunay bests the remaining
20\%. It is likely that with less data, Delaunay would be the best
performer.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-throughput.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Read Throughtput KS Statistic};
  \end{tikzpicture}
  \caption{Above, the models directly capable of predicting
    distributions are applied to predicting the expected CDF of I/O
    throughput at previously unseen system configurations. These
    boxes depict the median (middle bar), median $95\%$ confidence
    interval (cones), quartiles (box edges), fences at $3/2$
    interquartile range (whiskers), and outliers (dots) of KS
    statistic between the observed distribution at each system
    configuration and the predicted distribution. The above figure is
    \textit{not} log-scaled like figure \ref{fig:hist-throughput}. The
    complimentary numerical data for this figure is provided in
    Appendix table \ref{table:error-throughput}.}
  \label{fig:error-throughput}
\end{figure}

@@

\begin{table}
  \renewcommand{\arraystretch}{1.3}
  \centering
  \begin{tabular}{c|c|c|c|c}
     & $p$ = .05 & $p$ = .01 & $p$ = .001 & $p$ = 1.0e-6\\
    \hline
    Delaunay & $\mathbf{50.3}\%$ & $\mathit{43.5}\%$ & $\mathit{36.2}\%$ & $\mathit{24.7}\%$\\
    ShepMod & $\mathit{51.4}\%$ & $44.8\%$ & $38.1\%$ & $27.7\%$\\
    Voronoi & $52.6\%$ & $\mathbf{43.4}\%$ & $\mathbf{34.4}\%$ & $\mathbf{19.1}\%$\\
    BoxMesh & $99.5\%$ & $98.5\%$ & $96.6\%$ & $89.5\%$\\
  \end{tabular}
  \caption{This is the numerical counterpart to the histogram data
    presented in figure \ref{fig:throughput-prediction}. The columns
    display the percent of null hypothesis rejections by the KS-test
    when provided different selections of $p$-values for each
    algorithm. The algorithm with the lowest rejection rate at each
    $p$ is boldface, while the second lowest is italicized.}
  \label{table:null-hypothesis-results}
\end{table}

@@

Figure \ref{fig:throughput-prediction} expands on the KS statistic
results presented in figure \ref{fig:error-throughput}. Agglomerate
errors for each algorithm resemble a Gamma distribution. The
percentages of significant prediction errors with varying $p$-values
are on display in Table \ref{table:null-hypothesis-results}. When
considering the $p=0.001$ results for each technique, a little over
one third of the predicted CDFs are significantly different from the
measured (and presumed) correct CDFs. However, it should be noted that
with 150 samples, the error of an empirical distribution function
(EDF) can reasonably be upwards of $.1$, which serves as a rough
estimate for the lower limit of achievable error. Globally, only a
third of Voronoi predictions fail to capture \textit{all} of the
characteristics of the CDFs at new system configurations.

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    Algorithm & Avg. \% Best & Avg. Fit Time & Avg. App. Time (1)\\
    \hline
    MARS & $4.6\%$ & $22.3$s & $1.37 \times 10^{-3}$s\\
    SVR & $\mathit{21.1}\%$ & $0.503$s & $\mathit{1.37 \times 10^{-4}}$s\\
    MLP & $\mathbf{42.1}\%$ & $210.0$s & $1.02 \times 10^{-3}$s\\
    Delaunay & $6.0\%$ & $\mathbf{1.43 \times 10^{-4}}$s & $3.03$s\\
    ShepMod & $18.4\%$ & $0.711$s & $1.49 \times 10^{-4}$s\\
    LSHEP & $8.4\%$ & $1.69$s & $\mathbf{1.16 \times 10^{-4}}$s\\
    Voronoi & $0.5\%$ & $\mathit{0.127}$s & $0.0375$s\\
    BoxSplines & $0.2\%$ & $0.816$s & $5.26 \times 10^{-4}$s\\
    \hline
  \end{tabular}
  \caption{This data is the average of Appendix tables
    \ref{table:error-forest-fire}, \ref{table:error-parkinsons},
    \ref{table:error-weather}, \ref{table:error-credit-card}, and
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time-to-fit, and the average time
    required to approximated one point. Interpolants provide the
    lowest error approximation one third of the time across all data,
    while regressors occupy the other two thirds. This result is
    obtained without any customized tuning or preprocessing to
    maximize the performance of any given algorithm. In practice,
    tuning and preprocessing may have large effects on approximation
    performance.}
  \label{table:avg-performance}
\end{table}

@@

The various interpolants discussed in this paper have been
demonstrated to effectively approximate multivariate phenomena up to
$30$ dimensions. The underlying constructions are theoretically
straightforward, yet powerful and flexible. Most of the interpolants'
computational complexities make them particularly suitable for
applications in even higher dimension, where the major benefits are
seen when only a small number of approximations are to be made from
any given data ($\leq 1000$).

@@

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $0.00984$ & $3.11$ & $7.01$ & $\mathit{11.7}$ & $1090.0$\\
    SVR & $\mathit{0.00402}$ & $\mathbf{0.243}$ & $\mathbf{0.416}$ & $\mathbf{6.19}$ & $1090.0$\\
    MLP & $0.0426$ & $2.63$ & $\mathit{5.27}$ & $14.0$ & $1090.0$\\
    Delaunay & $\mathbf{0.00}$ & $1.98$ & $5.37$ & $13.1$ & $\mathit{1080.0}$\\
    ShepMod & $\mathbf{0.00}$ & $\mathit{1.93}$ & $6.27$ & $16.0$ & $1090.0$\\
    LSHEP & $0.0400$ & $2.17$ & $8.87$ & $19.1$ & $\mathbf{1070.0}$\\
    Voronoi & $0.00982$ & $3.65$ & $7.56$ & $15.6$ & $1090.0$\\
    BoxSpline & $\mathbf{0.00}$ & $2.27$ & $5.91$ & $16.4$ & $1090.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    figure \ref{fig:error-forest-fire}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $0.00948$ & $9.98$ & $20.4$ & $32.9$ & $863.0$\\
    SVR & $0.00138$ & $3.17$ & $7.31$ & $12.6$ & $\mathbf{27.5}$\\
    MLP & $2.39 \times 10^{-5}$ & $\mathit{0.533}$ & $\mathit{1.25}$ & $\mathbf{2.84}$ & $39.3$\\
    Delaunay & $\mathit{3.72 \times 10^{-12}}$ & $1.20$ & $3.50$ & $7.67$ & $30.7$\\
    ShepMod & $\mathbf{0.00}$ & $\mathbf{0.255}$ & $\mathbf{0.908}$ & $\mathit{3.43}$ & $34.5$\\
    LSHEP & $0.00254$ & $2.93$ & $7.16$ & $13.1$ & $\mathit{29.0}$\\
    Voronoi & $\mathbf{0.00}$ & $1.29$ & $3.52$ & $6.87$ & $30.1$\\
    BoxSpline & $0.00287$ & $4.39$ & $9.10$ & $14.8$ & $41.3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $\mathit{6.45 \times 10^{-15}}$ & $\mathbf{2.70 \times 10^{-14}}$ & $1.66$ & $1.96$ & $\mathit{53.3}$\\
    SVR & $0.0420$ & $0.143$ & $0.148$ & $\mathit{0.860}$ & $119.0$\\
    MLP & $6.89 \times 10^{-5}$ & $0.0337$ & $\mathbf{0.0795}$ & $\mathbf{0.264}$ & $\mathbf{5.31}$\\
    Delaunay & $\mathbf{0.00}$ & $0.187$ & $0.919$ & $2.72$ & $56.3$\\
    ShepMod & $\mathbf{0.00}$ & $0.0957$ & $0.685$ & $2.90$ & $73.2$\\
    LSHEP & $\mathbf{0.00}$ & $\mathit{0.0153}$ & $\mathit{0.106}$ & $1.17$ & $113.0$\\
    Voronoi & $\mathbf{0.00}$ & $0.430$ & $1.28$ & $2.94$ & $83.8$\\
    BoxSpline & $\mathbf{0.00}$ & $0.789$ & $2.06$ & $5.25$ & $119.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $5.36$ & $3610.0$ & $4580.0$ & $5450.0$ & $13400.0$\\
    SVR & $0.0138$ & $8.47$ & $15.4$ & $41.9$ & $7700.0$\\
    MLP & $0.00151$ & $\mathbf{1.60}$ & $\mathbf{3.86}$ & $\mathbf{8.34}$ & $\mathbf{604.0}$\\
    Delaunay & $\mathbf{0.00}$ & $\mathit{2.69}$ & $\mathit{13.8}$ & $\mathit{35.0}$ & $\mathit{4840.0}$\\
    ShepMod & $\mathbf{0.00}$ & $4.21$ & $17.3$ & $51.6$ & $6510.0$\\
    LSHEP & $1.27$ & $199.0$ & $260.0$ & $343.0$ & $6530.0$\\
    Voronoi & $\mathit{2.89 \times 10^{-10}}$ & $14.7$ & $32.8$ & $52.9$ & $4860.0$\\
    BoxSpline & $0.00740$ & $20.8$ & $40.9$ & $79.6$ & $7640.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    figure \ref{fig:error-credit-card}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-credit-card}
\end{table}

>>>>

The remainder of this paper is organized as follows. Sections
\ref{sec:regression} and \ref{sec:interpolation} present the
multivariate models. Section \ref{sec:error} gives the error measuring
methodology that is used for collecting empirical results. Section
\ref{sec:theory} presents the theoretical error bounds for
interpolation. Section \ref{sec:data} presents the data sets for
empirical approximation analysis and the approximation results for all
models on these data sets. Section \ref{sec:discussion} analyzes and
discusses the results, their implications, and their
limitations. Finally, Section \ref{sec:conclusion} concludes.

@@

This section presents the theoretical results bounding the error of
simplicial interpolation. The error analysis relies on simplicial
interpolation for three reasons: (1) second order results can be
obtained utilizing a Lipschitz constant on the gradient of a function,
rather than standard Lipschitz bounds; (2) the results directly
apply to Delaunay; and (3) multiple other interpolants in this paper
compute predictions as convex combinations of observed function
values, which may allow for straight forward extensions of this error
bound.

@@

In summary, the approximation error of a simplicial interpolant tends
quadratically towards zero when approaching observed data only when
the diameter of the simplex is also reduced at a proportional rate.
Only linear convergence to the true function can be achieved in
practice, without the incorporation of additional observations. Notice
that the approximation error is largely determined by the spacing of
observed data. Predictions made by simplices whose vertices are not
well-spaced (i.e. have large diameter, or are nearly contained in a
hyperplane) have higher error. In light of this error bound, an
empirical evaluation of presented algorithms follows.

@@

The theoretical results constructed in Section \ref{sec:theory} for
simplicial interpolation are promising, however they are difficult to
interpret in context with approximation algorithms that do not have
similar known uniform error bounds. For that reason, this paper
utilizes five different data sets of varying dimension and application
to construct approximations and compare the accuracy of different
techniques.

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-forest-fire.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Area Burned Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the amount of area
    that would be burned given environment conditions. $10$-fold
    cross validation as described in the beginning of Section
    \ref{sec:data} is used to evaluated each algorithm. This results
    in exactly one prediction from each algorithm for each data
    point. These boxes depict the median (middle bar), median $95\%$
    confidence interval (cones), quartiles (box edges), fences at
    $3/2$ interquartile range (whiskers), and outliers (dots) of
    absolute prediction error for each model. Similar to figure
    \ref{fig:hist-forest-fire}, the errors are presented on a natural
    log scale. The complementing numerical data to this figure is
    provided in Table \ref{table:error-forest-fire} in the Appendix.}
  \label{fig:error-forest-fire}
\end{figure}

@@

As suggested by Figure \ref{fig:error-forest-fire}, the SVR has the
lowest absolute prediction errors for 80\% of the data, with ShepMod
and BoxSpline being the nearest overall competitors. The effectiveness
of SVR on this data suggests the underlying function can be defined by
relatively few parameters, as well as the importance of capturing the
low-burn-area data points.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-weather.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Sydney Rainfall Tomorrow Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the amount of
    rainfall expected on the next calendar day given various sources
    of local meteorological data. $10$-fold cross validation as
    described in the beginning of Section \ref{sec:data} is used to
    evaluated each algorithm. This results in exactly one prediction
    from each algorithm for each data point. These boxes depict the
    median (middle bar), median $95\%$ confidence interval (cones),
    quartiles (box edges), fences at $3/2$ interquartile range
    (whiskers), and outliers (dots) of absolute prediction error for
    each model. The errors are presented on a natural log scale,
    mimicking the presentation in Figure \ref{fig:hist-weather}. The
    complementing numerical data to this figure is provided in table
    \ref{table:error-weather} in the Appendix.}
  \label{fig:error-weather}
\end{figure}

@@

While Figure \ref{fig:hist-weather} makes MARS look far better than
other techniques, it only provides the best prediction for 11\% of
points. The MLP has the lowest absolute error for 56\% of points and
LSHEP is best for 28\%. MARS likely achieves such a low first quartile
due to the high occurrence of the value 0 in the data.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-credit-card.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Transaction Amount Error};
  \end{tikzpicture}
  \caption{All models are applied to approximate the expected
    transaction amount given transformed (and obfuscated) vendor and
    customer-descriptive features. $10$-fold cross validation as
    described in the beginning of Section \ref{sec:data} is used to
    evaluated each algorithm. This results in exactly one prediction
    from each algorithm for each data point. These boxes depict the
    median (middle bar), median $95\%$ confidence interval (cones),
    quartiles (box edges), fences at $3/2$ interquartile range
    (whiskers), and outliers (dots) of absolute prediction error for
    each model. The absolute errors in transaction amount predictions
    are presented on a natural log scale, just as in figure
    \ref{fig:hist-credit-card}. The complementing numerical data to
    this figure is provided in Table \ref{table:error-credit-card} in
    the Appendix.}
  \label{fig:error-credit-card}
\end{figure}

@@

As can be seen in Figure \ref{fig:error-credit-card}, the MLP
outperforms all other algorithms at the first, second, third, and
fourth quartiles. The MLP produces the lowest absolute error
prediction for 80\% of transactions, Delaunay bests the remaining
20\%. It is likely that with less data, Delaunay would be the best
performer.
%% -------------------------------------------------------------------

@@

\begin{figure}
  \centering
  \begin{tikzpicture}
    \node (img)  {\includegraphics[width=0.8\textwidth,]{Figures/error-box-throughput.pdf}};
    \node[below=of img, node distance=1cm, yshift=1cm] {Read Throughtput KS Statistic};
  \end{tikzpicture}
  \caption{Above, the models directly capable of predicting
    distributions are applied to predicting the expected CDF of I/O
    throughput at previously unseen system configurations. These
    boxes depict the median (middle bar), median $95\%$ confidence
    interval (cones), quartiles (box edges), fences at $3/2$
    interquartile range (whiskers), and outliers (dots) of KS
    statistic between the observed distribution at each system
    configuration and the predicted distribution. The above figure is
    \textit{not} log-scaled like Figure \ref{fig:hist-throughput}. The
    complimentary numerical data for this figure is provided in
    Appendix Table \ref{table:error-throughput}.}
  \label{fig:error-throughput}
\end{figure}

@@

\begin{table}
  \renewcommand{\arraystretch}{1.3}
  \centering
  \begin{tabular}{c|c|c|c|c}
     & $p$ = .05 & $p$ = .01 & $p$ = .001 & $p$ = 1.0e-6\\
    \hline
    Delaunay & $\mathbf{50.3}\%$ & $\mathit{43.5}\%$ & $\mathit{36.2}\%$ & $\mathit{24.7}\%$\\
    ShepMod & $\mathit{51.4}\%$ & $44.8\%$ & $38.1\%$ & $27.7\%$\\
    Voronoi & $52.6\%$ & $\mathbf{43.4}\%$ & $\mathbf{34.4}\%$ & $\mathbf{19.1}\%$\\
    BoxMesh & $99.5\%$ & $98.5\%$ & $96.6\%$ & $89.5\%$\\
  \end{tabular}
  \caption{This is the numerical counterpart to the histogram data
    presented in Figure \ref{fig:throughput-prediction}. The columns
    display the percent of null hypothesis rejections by the KS-test
    when provided different selections of $p$-values for each
    algorithm. The algorithm with the lowest rejection rate at each
    $p$ is boldface, while the second lowest is italicized.}
  \label{table:null-hypothesis-results}
\end{table}

@@

Figure \ref{fig:throughput-prediction} expands on the KS statistic
results presented in Figure \ref{fig:error-throughput}. Agglomerate
errors for each algorithm resemble a Gamma distribution. The
percentages of significant prediction errors with varying $p$-values
are on display in Table \ref{table:null-hypothesis-results}. When
considering the $p=0.001$ results for each technique, a little over
one third of the predicted CDFs are significantly different from the
measured (and presumed) correct CDFs. However, it should be noted that
with 150 samples, the error of an empirical distribution function
(EDF) can reasonably be upwards of $.1$, which serves as a rough
estimate for the lower limit of achievable error. Globally, only a
third of Voronoi predictions fail to capture \textit{all} of the
characteristics of the CDFs at new system configurations.

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c}
    \hline
    Algorithm & Avg. \% Best & Avg. Fit Time & Avg. App. Time (1)\\
    \hline
    MARS & $4.6\%$ & $22.3$s & $1.37 \times 10^{-3}$s\\
    SVR & $\mathit{21.1}\%$ & $0.503$s & $\mathit{1.37 \times 10^{-4}}$s\\
    MLP & $\mathbf{42.1}\%$ & $210.0$s & $1.02 \times 10^{-3}$s\\
    Delaunay & $6.0\%$ & $\mathbf{1.43 \times 10^{-4}}$s & $3.03$s\\
    ShepMod & $18.4\%$ & $0.711$s & $1.49 \times 10^{-4}$s\\
    LSHEP & $8.4\%$ & $1.69$s & $\mathbf{1.16 \times 10^{-4}}$s\\
    Voronoi & $0.5\%$ & $\mathit{0.127}$s & $0.0375$s\\
    BoxSplines & $0.2\%$ & $0.816$s & $5.26 \times 10^{-4}$s\\
    \hline
  \end{tabular}
  \caption{This data is the average of Appendix tables
    \ref{table:error-forest-fire}, \ref{table:error-parkinsons},
    \ref{table:error-weather}, \ref{table:error-credit-card}, and
    provides a gross summary of overall results. The columns display
    (weighted equally by data set, \textit{not} points) the average
    frequency with which any algorithm provided the lowest absolute
    error approximation, the average time-to-fit, and the average time
    required to approximate one point. Interpolants provide the
    lowest error approximation one third of the time across all data,
    while regressors occupy the other two thirds. This result is
    obtained without any customized tuning or preprocessing to
    maximize the performance of any given algorithm. In practice,
    tuning and preprocessing may have large effects on approximation
    performance.}
  \label{table:avg-performance}
\end{table}

@@

The various interpolants discussed in this paper have been
demonstrated to effectively approximate multivariate phenomena in up
to $30$ dimensions. The underlying constructions are theoretically
straightforward, yet powerful and flexible. Most of the interpolants'
computational complexities make them particularly suitable for
applications in even higher dimension. The major benefits of
interpolation are seen when only a small number of approximations
($\leq 1000$) are made from data and when there are relatively few
data points for the dimension (for empirical results presented, $\log_d n \leq 5$).

@@

\newpage

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $0.00984$ & $3.11$ & $7.01$ & $\mathit{11.7}$ & $1090.0$\\
    SVR & $\mathit{0.00402}$ & $\mathbf{0.243}$ & $\mathbf{0.416}$ & $\mathbf{6.19}$ & $1090.0$\\
    MLP & $0.0426$ & $2.63$ & $\mathit{5.27}$ & $14.0$ & $1090.0$\\
    Delaunay & $\mathbf{0.00}$ & $1.98$ & $5.37$ & $13.1$ & $\mathit{1080.0}$\\
    ShepMod & $\mathbf{0.00}$ & $\mathit{1.93}$ & $6.27$ & $16.0$ & $1090.0$\\
    LSHEP & $0.0400$ & $2.17$ & $8.87$ & $19.1$ & $\mathbf{1070.0}$\\
    Voronoi & $0.00982$ & $3.65$ & $7.56$ & $15.6$ & $1090.0$\\
    BoxSpline & $\mathbf{0.00}$ & $2.27$ & $5.91$ & $16.4$ & $1090.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-forest-fire}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-forest-fire}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $0.00948$ & $9.98$ & $20.4$ & $32.9$ & $863.0$\\
    SVR & $0.00138$ & $3.17$ & $7.31$ & $12.6$ & $\mathbf{27.5}$\\
    MLP & $2.39 \times 10^{-5}$ & $\mathit{0.533}$ & $\mathit{1.25}$ & $\mathbf{2.84}$ & $39.3$\\
    Delaunay & $\mathit{3.72 \times 10^{-12}}$ & $1.20$ & $3.50$ & $7.67$ & $30.7$\\
    ShepMod & $\mathbf{0.00}$ & $\mathbf{0.255}$ & $\mathbf{0.908}$ & $\mathit{3.43}$ & $34.5$\\
    LSHEP & $0.00254$ & $2.93$ & $7.16$ & $13.1$ & $\mathit{29.0}$\\
    Voronoi & $\mathbf{0.00}$ & $1.29$ & $3.52$ & $6.87$ & $30.1$\\
    BoxSpline & $0.00287$ & $4.39$ & $9.10$ & $14.8$ & $41.3$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-parkinsons}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum of each column is boldface, while the second lowest value
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-parkinsons}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $\mathit{6.45 \times 10^{-15}}$ & $\mathbf{2.70 \times 10^{-14}}$ & $1.66$ & $1.96$ & $\mathit{53.3}$\\
    SVR & $0.0420$ & $0.143$ & $0.148$ & $\mathit{0.860}$ & $119.0$\\
    MLP & $6.89 \times 10^{-5}$ & $0.0337$ & $\mathbf{0.0795}$ & $\mathbf{0.264}$ & $\mathbf{5.31}$\\
    Delaunay & $\mathbf{0.00}$ & $0.187$ & $0.919$ & $2.72$ & $56.3$\\
    ShepMod & $\mathbf{0.00}$ & $0.0957$ & $0.685$ & $2.90$ & $73.2$\\
    LSHEP & $\mathbf{0.00}$ & $\mathit{0.0153}$ & $\mathit{0.106}$ & $1.17$ & $113.0$\\
    Voronoi & $\mathbf{0.00}$ & $0.430$ & $1.28$ & $2.94$ & $83.8$\\
    BoxSpline & $\mathbf{0.00}$ & $0.789$ & $2.06$ & $5.25$ & $119.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-weather}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-weather}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{c|c|c|c|c|c}
    \hline
    Algorithm & Min & $25^{th}$ & $50^{th}$ & $75^{th}$ & Max\\
    \hline
    MARS & $5.36$ & $3610.0$ & $4580.0$ & $5450.0$ & $13400.0$\\
    SVR & $0.0138$ & $8.47$ & $15.4$ & $41.9$ & $7700.0$\\
    MLP & $0.00151$ & $\mathbf{1.60}$ & $\mathbf{3.86}$ & $\mathbf{8.34}$ & $\mathbf{604.0}$\\
    Delaunay & $\mathbf{0.00}$ & $\mathit{2.69}$ & $\mathit{13.8}$ & $\mathit{35.0}$ & $\mathit{4840.0}$\\
    ShepMod & $\mathbf{0.00}$ & $4.21$ & $17.3$ & $51.6$ & $6510.0$\\
    LSHEP & $1.27$ & $199.0$ & $260.0$ & $343.0$ & $6530.0$\\
    Voronoi & $\mathit{2.89 \times 10^{-10}}$ & $14.7$ & $32.8$ & $52.9$ & $4860.0$\\
    BoxSpline & $0.00740$ & $20.8$ & $40.9$ & $79.6$ & $7640.0$\\
    \hline
  \end{tabular}
  \caption{This numerical data accompanies the visual provided in
    Figure \ref{fig:error-credit-card}. The columns of absolute error
    percentiles correspond to the minimum, first quartile, median,
    second quartile, and maximum absolute errors respectively. The
    minimum value of each column is boldface, while the second lowest
    is italicized. All values are rounded to three significant
    digits.}
  \label{table:error-credit-card}
\end{table}
